### 2014-11-12 form.tex
before replacement math mode by equation environments

\paragraph{Semantics for accessors (may mutate $S$, do not change the nonexpired mappings)}
\begin{itemize}
   \item[has]
     \begin{itemize}
       \item $\o{has}_t(m \in M, k \in K) ~\Leftrightarrow~ \exists [k,v,e] \in m.\s{mapping}_t \wedge o_t=\o{has}_t(m, k)$\\
       \item It does not change nonexpired mappings:
         $$o_t \simeq \o{has}_t(m, k) ~\Leftrightarrow~ \p{const}_t(m)$$
     \end{itemize}
     \item[get]
       \begin{itemize}
         \item One can get a mapping only if it exists in the map:
           $$\o{get}_t(m \in M, k \in K) \rightarrow fail ~\Leftrightarrow~ [k,v,e] \not\in m.\s{mapping}_t \wedge o_t=\o{get}_t(m, k)$$
           $$(v\in V,e\in \nintset)\gets \o{get}_t(m \in M, k \in K) ~\Leftrightarrow~ \exists [k,v,e] \in m.\s{mapping}_t \wedge o_t=\o{get}_t(m, k)$$
         \item In anyway, it does not change existing unexpired mappings:
           $$o_t \simeq \o{get}_t(m, k) ~\Leftrightarrow~ \p{const}_t(m)$$
       \end{itemize}
\end{itemize}

\paragraph{Semantics for operations that mutate state}
\begin{itemize}
  \item[constructor]
    \begin{itemize}
      \item The constructor forms a new empty map \\
        $m \gets \o{constructor}_0(s \in \nintset) \Leftrightarrow \p{empty}_0(m) \wedge \forall t \in \nintset m.\s{maxSize}_t=s$
      \item The constructor must be called once and only once, at the very beginning of $\tau$ (i.e., $\tau$ contains no other constructor call after the first one) \\
        $o_0 \equiv \o{constructor}_0 \wedge (\forall t\in \moreset{1} \Rightarrow o_t \neq \o{constructor}_t)$ 

@@

  \item[erase]
    \begin{itemize}
      \item ``Erase'' deletes an entry with a given key. If the entry does not exist in the \p{mapping}, it fails. It does not change other mappings if they are not expired.
        $$\Big(o_t \simeq \o{erase}_t(m\in M, k\in K) ~\Leftrightarrow~ \p{isolated}_t(m, k)\Big) \wedge$$
      \item If there was a such mapping for $k$, ``erase'' will remove it.
        $$\Big(x=\o{erase}_t(m\in M, k\in K) \wedge \exists [k, v, e] \in m.\s{mapping}_{t-1} ~\Leftrightarrow~$$
        $$x=success \wedge \big(\forall v'\in V, e'\in \nintset \Rightarrow [k, v', e'] \not\in m.\s{mapping}_t\big) \wedge m.\s{size}_t \le m.\s{size}_{t-1}-1 \Big) \wedge$$
      \item If there was not --- it will fail. 
        $$\Big(x=\o{erase}_t(m\in M, k\in K) \wedge [k,v,e]\not\in m.\s{mapping}_{t-1} ~\Leftrightarrow~$$
        $$x=fail \wedge \p{const}_t(m)\Big)$$
    \item[put]
      \begin{itemize}
        \item ``Put'' inserts a new mapping, if the number of unexpired elements is less than \s{maxSize} and there is no unexpired entry with the same key.
          This function does not touch any unexpired entry with key other than $k$.
          $$\Big(o_t \simeq \o{put}_t(m\in M, k\in K, v\in V, e\in \moreset{t}) ~\Leftrightarrow~ \p{isolated}_t(m, k)\Big) \wedge$$
        \item If there was no such mupping before, and there is enough room, it will succeed.
          $$\Big(x=\o{put}_t(m, k, v, e) \wedge m.\s{size}_{t-1} < m.\s{maxSize}_{t-1} \wedge \big(\forall v'\in V, e'\in \nintset \Rightarrow [k, v', e'] \not\in m.\s{mapping}_{t-1}\big) \Leftrightarrow $$
          $$ x=success \wedge m.\s{size}_t \le m.\s{size}_{t-1}+1 \wedge [k, v, e] \in m.\s{mapping}_t\Big)\wedge$$
        \item If a mapping with key $k$ allready exists, and it does not expires on $t$, put will fail.
          $$\Big(x=\o{put}_t(m, k, v, e) \wedge \big(\exists v'\in V, e'\in \nintset: [k, v', e']\in m.\s{mapping}_{t-1} \wedge e > t \big) \Leftrightarrow$$
          $$x=fail \wedge \p{const}_t(m)\Big)\wedge$$
        \item If a mapping with key $k$ expires on $t$, put will replace it:
          $$\Big(x=\o{put}_t(m, k, v, e) \wedge \big(\exists v'\in V: [k, v', t]\in m.\s{mapping}_{t-1}\big) \Leftrightarrow$$
          $$ x=success \wedge m.\s{size}_t \le m.\s{size}_{t-1} \wedge [k, v, e] \in m.\s{mapping}_t\Big)\wedge$$
        \item If there is no room, but some mappings expire on $t$, put will succed:
          $$\Big(x=\o{put}_t(m, k, v, e) \wedge m.\s{size}_{t-1} = m.\s{maxSize}_{t-1} \wedge [k, v, e] \not\in m.\s{mapping}_{t-1} \wedge $$
          $$\big(\exists k'\in K, v'\in V: [k', v', t] \in m.\s{mapping}_{t-1}\big) \Leftrightarrow$$
          $$x=success \wedge m.\s{state}_t \le m.\s{state}_{t-1} \wedge [k, v, t] \in m.\s{mapping}_t\Big)\wedge$$
        \item If there is no room, and no mappings expire on $t$, put will fail:
          $$\Big(x=\o{put}_t(m, k, v, e) \wedge m.\s{size}_{t-1} = m.\s{maxSize}_{t-1} \wedge $$
          $$\big(\forall k'\in K, v'\in V, e' \in \nintset: [k', v', e'] \in m.\s{mapping}_{t-1} \Rightarrow e' > t \big) \Leftrightarrow$$
          $$x=fail \wedge \p{const}_t(m)\Big)$$
%        \item If there is no room, but some mappings have expired, one still can put.
%          $$\Big(x=\o{put}_t(m, k, v, e) \wedge m.\s{size}_{t-1} = m.\s{maxSize}_{t-1} \wedge \neg\o{has}_{t-1}(m, k) \wedge$$
%          $$\big(\exists k'\in K, e'\in \nintset: \o{has}_{t-1}(m,k')\wedge (\cdot,e')=\o{get}_{t-1}(m, k) \wedge e'<t \big) \Leftrightarrow$$
%          $$x=success \wedge \o{has}_t(m, k)\wedge\o{get}_t(m, k) = (v, e)\Big)\wedge$$

%          $$\Big(x=\o{put}_t(m, k, v, e) \wedge m.\s{size}_{t-1} = m.\s{maxSize}_{t-1} \wedge \neg\o{has}_{t-1}(m, k) \wedge$$
%          $$\big(\exists k'\in K, e'\in \nintset: \o{has}_{t-1}(m,k')\wedge (\cdot,e')=\o{get}_{t-1}(m, k) \wedge e'<t \big) \Leftrightarrow$$
%          $$x=success \wedge \o{has}_t(m, k)\wedge\o{get}_t(m, k) = (v, e)\Big)\wedge$$
%        \item If there is an unexpired mapping with the same key, put will fail.
%          $$\Big(x=\o{put}_t(m, k, v, e) \wedge \o{has}_{t-1}(m, k) \wedge (v, e)=\o{get}_{t-1}(m, k) \wedge e \ge t \Leftrightarrow$$
%          $$x=fail \wedge m.\s{size}_t \le m.\s{size}_{t-1} \wedge \o{has}_t(m, k) \wedge \o{get}_t(m, k) = (v, e)\Big)\wedge$$
%        \item Into full map, one can not put any more keys.
%          $$\Big(x=\o{put}_t(m, k, v, e) \wedge$$
%          $$\big(\forall k'\in K,e'\in \nintset :\o{has}_{t-1}(m, k')\wedge(\cdot,e')=\o{get}_{t-1}(m,k') \Rightarrow e' \ge t \big) \wedge m.\s{size}_{t-1} = m.\s{maxSize}_{t-1} \Leftrightarrow$$
%          $$x=fail \wedge m.\s{size}_t = m.\s{size}_{t-1} \wedge \p{const}_t(m, k)\Big)\wedge$$
      \end{itemize}

\paragraph{Properties to be proven}
\begin{itemize}
  \item $\p{empty}_t(m) \Leftrightarrow m.\s{size}_t=0$
  \item If the map is empty, there no keys in it:
    $$m.\s{size}_t=0 \Rightarrow \forall k\in K \o{has}_t(m, k) = false $$
  \item $\o{has}_t(m, k) \Leftrightarrow \o{get}_t(m, k) \not\rightarrow fail$

@@

>>>>

\paragraph{Semantics for accessors (may mutate $S$, do not change the nonexpired mappings)}
\begin{itemize}
   \item[has]
     \begin{itemize}
       \item $\o{has}_t(m \in M, k \in K) ~\Leftrightarrow~ \exists [k,v,e] \in m.\s{mapping}_t \wedge o_t=\o{has}_t(m, k)$\\
       \item It does not change nonexpired mappings:
         \begin{equation}
           o_t \simeq \o{has}_t(m, k) ~\Leftrightarrow~ \p{const}_t(m)
         \end{equation}
     \end{itemize}
     \item[get]
       \begin{itemize}
         \item One can get a mapping only if it exists in the map:
           $$\o{get}_t(m \in M, k \in K) \rightarrow fail ~\Leftrightarrow~ [k,v,e] \not\in m.\s{mapping}_t \wedge o_t=\o{get}_t(m, k)$$
           $$(v\in V,e\in \nintset)\gets \o{get}_t(m \in M, k \in K) ~\Leftrightarrow~ \exists [k,v,e] \in m.\s{mapping}_t \wedge o_t=\o{get}_t(m, k)$$
         \item In anyway, it does not change existing unexpired mappings:
           $$o_t \simeq \o{get}_t(m, k) ~\Leftrightarrow~ \p{const}_t(m)$$
       \end{itemize}
\end{itemize}

\paragraph{Semantics for operations that mutate state}
\begin{itemize}
  \item[constructor]
    \begin{itemize}
      \item The constructor forms a new empty map \\
        $m \gets \o{constructor}_0(s \in \nintset) \Leftrightarrow \p{empty}_0(m) \wedge \forall t \in \nintset m.\s{maxSize}_t=s$
      \item The constructor must be called once and only once, at the very beginning of $\tau$ (i.e., $\tau$ contains no other constructor call after the first one) \\
        $o_0 \equiv \o{constructor}_0 \wedge (\forall t\in \moreset{1} \Rightarrow o_t \neq \o{constructor}_t)$ 
    \end{itemize}
  \item[erase]
    \begin{itemize}
      \item ``Erase'' deletes an entry with a given key. If the entry does not exist in the \p{mapping}, it fails. It does not change other mappings if they are not expired.
        $$\Big(o_t \simeq \o{erase}_t(m\in M, k\in K) ~\Leftrightarrow~ \p{isolated}_t(m, k)\Big) \wedge$$
      \item If there was a such mapping for $k$, ``erase'' will remove it.
        $$\Big(x=\o{erase}_t(m\in M, k\in K) \wedge \exists [k, v, e] \in m.\s{mapping}_{t-1} ~\Leftrightarrow~$$
        $$x=success \wedge \big(\forall v'\in V, e'\in \nintset \Rightarrow [k, v', e'] \not\in m.\s{mapping}_t\big) \wedge m.\s{size}_t \le m.\s{size}_{t-1}-1 \Big) \wedge$$
      \item If there was not --- it will fail. 
        $$\Big(x=\o{erase}_t(m\in M, k\in K) \wedge [k,v,e]\not\in m.\s{mapping}_{t-1} ~\Leftrightarrow~$$
        $$x=fail \wedge \p{const}_t(m)\Big)$$
    \end{itemize}
    \item[put]
      \begin{itemize}
        \item ``Put'' inserts a new mapping, if the number of unexpired elements is less than \s{maxSize} and there is no unexpired entry with the same key.
          This function does not touch any unexpired entry with key other than $k$.
          $$\Big(o_t \simeq \o{put}_t(m\in M, k\in K, v\in V, e\in \moreset{t}) ~\Leftrightarrow~ \p{isolated}_t(m, k)\Big) \wedge$$
        \item If there was no such mupping before, and there is enough room, it will succeed.
          $$\Big(x=\o{put}_t(m, k, v, e) \wedge m.\s{size}_{t-1} < m.\s{maxSize}_{t-1} \wedge \big(\forall v'\in V, e'\in \nintset \Rightarrow [k, v', e'] \not\in m.\s{mapping}_{t-1}\big) \Leftrightarrow $$
          $$ x=success \wedge m.\s{size}_t \le m.\s{size}_{t-1}+1 \wedge [k, v, e] \in m.\s{mapping}_t\Big)\wedge$$
        \item If a mapping with key $k$ allready exists, and it does not expires on $t$, put will fail.
          $$\Big(x=\o{put}_t(m, k, v, e) \wedge \big(\exists v'\in V, e'\in \nintset: [k, v', e']\in m.\s{mapping}_{t-1} \wedge e > t \big) \Leftrightarrow$$
          $$x=fail \wedge \p{const}_t(m)\Big)\wedge$$
        \item If a mapping with key $k$ expires on $t$, put will replace it:
          $$\Big(x=\o{put}_t(m, k, v, e) \wedge \big(\exists v'\in V: [k, v', t]\in m.\s{mapping}_{t-1}\big) \Leftrightarrow$$
          $$ x=success \wedge m.\s{size}_t \le m.\s{size}_{t-1} \wedge [k, v, e] \in m.\s{mapping}_t\Big)\wedge$$
        \item If there is no room, but some mappings expire on $t$, put will succeed:
          $$\Big(x=\o{put}_t(m, k, v, e) \wedge m.\s{size}_{t-1} = m.\s{maxSize}_{t-1} \wedge [k, v, e] \not\in m.\s{mapping}_{t-1} \wedge $$
          $$\big(\exists k'\in K, v'\in V: [k', v', t] \in m.\s{mapping}_{t-1}\big) \Leftrightarrow$$
          $$x=success \wedge m.\s{state}_t \le m.\s{state}_{t-1} \wedge [k, v, t] \in m.\s{mapping}_t\Big)\wedge$$
        \item If there is no room, and no mappings expire on $t$, put will fail:
          $$\Big(x=\o{put}_t(m, k, v, e) \wedge m.\s{size}_{t-1} = m.\s{maxSize}_{t-1} \wedge $$
          $$\big(\forall k'\in K, v'\in V, e' \in \nintset: [k', v', e'] \in m.\s{mapping}_{t-1} \Rightarrow e' > t \big) \Leftrightarrow$$
          $$x=fail \wedge \p{const}_t(m)\Big)$$
      \end{itemize}

@@

\paragraph{Properties to be proven}
\begin{itemize}
  \item $\p{empty}_t(m) \Leftrightarrow m.\s{size}_t=0$
  \item If the map is empty, there no keys in it:
    $$m.\s{size}_t=0 \Leftrightarrow \forall k\in K \o{has}_t(m, k) = false $$
  \item $\o{has}_t(m, k) \Leftrightarrow \o{get}_t(m, k) \not\rightarrow fail$

@@

%        \item If there is no room, but some mappings have expired, one still can put.
%          $$\Big(x=\o{put}_t(m, k, v, e) \wedge m.\s{size}_{t-1} = m.\s{maxSize}_{t-1} \wedge \neg\o{has}_{t-1}(m, k) \wedge$$
%          $$\big(\exists k'\in K, e'\in \nintset: \o{has}_{t-1}(m,k')\wedge (\cdot,e')=\o{get}_{t-1}(m, k) \wedge e'<t \big) \Leftrightarrow$$
%          $$x=success \wedge \o{has}_t(m, k)\wedge\o{get}_t(m, k) = (v, e)\Big)\wedge$$

%          $$\Big(x=\o{put}_t(m, k, v, e) \wedge m.\s{size}_{t-1} = m.\s{maxSize}_{t-1} \wedge \neg\o{has}_{t-1}(m, k) \wedge$$
%          $$\big(\exists k'\in K, e'\in \nintset: \o{has}_{t-1}(m,k')\wedge (\cdot,e')=\o{get}_{t-1}(m, k) \wedge e'<t \big) \Leftrightarrow$$
%          $$x=success \wedge \o{has}_t(m, k)\wedge\o{get}_t(m, k) = (v, e)\Big)\wedge$$
%        \item If there is an unexpired mapping with the same key, put will fail.
%          $$\Big(x=\o{put}_t(m, k, v, e) \wedge \o{has}_{t-1}(m, k) \wedge (v, e)=\o{get}_{t-1}(m, k) \wedge e \ge t \Leftrightarrow$$
%          $$x=fail \wedge m.\s{size}_t \le m.\s{size}_{t-1} \wedge \o{has}_t(m, k) \wedge \o{get}_t(m, k) = (v, e)\Big)\wedge$$
%        \item Into full map, one can not put any more keys.
%          $$\Big(x=\o{put}_t(m, k, v, e) \wedge$$
%          $$\big(\forall k'\in K,e'\in \nintset :\o{has}_{t-1}(m, k')\wedge(\cdot,e')=\o{get}_{t-1}(m,k') \Rightarrow e' \ge t \big) \wedge m.\s{size}_{t-1} = m.\s{maxSize}_{t-1} \Leftrightarrow$$
%          $$x=fail \wedge m.\s{size}_t = m.\s{size}_{t-1} \wedge \p{const}_t(m, k)\Big)\wedge$$
